---
title: "Day2"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library()
```
--- Day 2: Password Philosophy ---
Debug the incorrect passwords. 

The rules are as follows. 

How many passwords are valid according to their policies?

I've saved my day2 input as a txt file. 

Doing another `data.table` solution as I've been spending too much time in the tidyverse and don't want those skills to atrophy. 

Part One is just some string splitting and counting
```{r}
day2 = fread("/Users/annaleigh/Documents/GitHub/advent_of_code/2020/input/day_two.txt",header = F)

day2[,c("min","max") := tstrsplit(V1,"-")]
day2[,min := as.numeric(min)]
day2[,max := as.numeric(max)]

day2[,required_letter := gsub(":","",V2)]

day2[, count_req_let := lengths(regmatches(V3, gregexpr(required_letter, V3))), by = 1:nrow(day2)]
part_one_ans = nrow(day2[count_req_let <= max & count_req_let >= min])
```

The correct number of passwords in my solution is `r part_one_ans`

Part Two

We'll take the table from above and use the `xor` operator
```{r}
day2[,let_min := substr(V3, min, min)]
day2[,let_max := substr(V3, max, max)]
part_two_ans = nrow(day2[xor(let_min == required_letter, let_max == required_letter)])
```

The correct number of passwords in my solution is `r part_two_ans`
